Board Game Recommendation

### 2015-04-01 paper.Rnw
Final edits and citations

\hh{Refer to table~\ref{tab:classifiers} somewhere in the text, add a label to the ratings table as well.}
<<classifiers, echo = FALSE, results = 'asis'>>=
print(xtable(paper_stuff$classifiers, caption = c("Example lines of classifiers data, as seen in Database", "Classifiers Table"), label="tab:classifiers"), include.rownames =FALSE )
@

@@

Define $C_{u,z}$ to the be the classifier score for user $u$ for classifier $z$ where $z$ is an index of the 1,851 classifiers. Then: \hh{XXX something went wrong with the formula ... not sure how to fix it}

@@

\hh{XXX why do those weights make sense? aren't those weights tilted towards players who are negatively correlated? are there any? (then it's not  a practical problem, even though still a theoretical one) just check that it is not supposed to be $1 - \rho$ in the denominator. I'm pretty sure that's what's it supposed to be.}
The weights for this will be $(1 + \rho_{u,k})^{-1}$ where $\rho_{u,k}$ is the correlation between user $u$ and user $k$. The number of neighbors to use $k$ will be determined by cross-validation on a user-to-user basis. In the end $z_{u,i}$ will be the \hh{weighted average of the} k-nearest-neighbors \hh{scores} for user $u$ and game $i$, as given in the equation below (where $u_{[j]}$ is the user with the $j^{\text{th}}$ highest correlation between themselves and user $u$):

\begin{equation}
z_{u,i} = \frac{\sum_{j = 1}^{k} \epsilon_{u_{[j]},i}^{(3)} \cdot \frac{1}{1 + \rho_{u,u_{[j]}}}}{\sum_{j = 1}^{k}\frac{1}{1 + \rho_{u,u_{[j]}}}}
\end{equation}

\subsubsection{Back to Rating}
From what we've produced above \hh{XXX to be more specific use the relevant equation numbers that are involved }, of the estimated rating for user $u$ and game $i$ is given by:

@@

The optimization will use ten-fold cross validation, wherein the data is randomly divided into 10 separate sections of roughly equal size. Then for each of the 10 sections, we'll treat the section as a test set and the other 9 to use as a training set. $\widehat{\theta}_g$ is fit first, and then from a grid of $\alpha_{game}$ values (where $\alpha_{game} \in [1,10000]$), a value of $\widehat{\theta}_i$ is produced for each of the $\alpha_{game}$ in the grid. For each of the $\widehat{\theta}_i$ that are estimated, we'll use the section that wasn't in the training set, the RMSE is calculated here by: \hh{XXX I am not sure this really is the RMSE - where did the squaring and the square rooting go?}
\begin{equation}
\text{RMSE} = \frac{ \sum r_{u,i}^{(1)} - (\theta_g + \theta_i)}{n}
\end{equation}

@@

\begin{figure}\centering
<<k_optim, echo = F, out.width='0.45\\textwidth'>>=
load("k_plot")
k_plot
@
\caption{\label{fig:k} \hh{You still need a caption here.}}
\end{figure}

\section{Technical Implementation} \hh{give references for R (to be a nice R user), shiny, and the other packages that you are using. citation() and citation("packagename") makes your life easy with that.}
This algorithm is implemented in R  using shiny as a vehicle for a simple, easy to use user interface. Behind the scenes, the data is stored in a data base with six tables: A player key table, which relates the players information to a unique player userid; A game key table, which relates game information to a unique game id; A ratings table which stores the ratings (a score from 1-10) along with the userid of the person who rated it and the game id which the rating is for; the classifiers table, relates the game id to characteristics about the game that will be useful in the classifier aggregation and k-nearest-neighbors section; the predicted ratings table, which will store predicted ratings if ratings have already been fit for a particular user; and the aggregated classifier ratings for each user. This data storage will allow for ease of implementation: we only really need the ratings table and the classifier table to do all the work, and the key tables are really only needed to display the information to the user in a format which they will understand.

@@

\begin{figure}\centering
<<subdom_plot, echo = FALSE, fig.width = 4, fig.height = 4, out.width='0.5\\textwidth'>>=
load("classifiers_plot")
out
@
\caption{\label{fig:subdplot} A player preference plot for subdomains for the user cwmassey.  \hh{XXX fix the y label, if showing it}}
\end{figure}

>>>>

% \hh{Refer to table~\ref{tab:classifiers} somewhere in the text, add a label to the ratings table as well.}
<<classifiers, echo = FALSE, results = 'asis'>>=
print(xtable(paper_stuff$classifiers, caption = c("Example lines of classifiers data, as seen in Database", "Classifiers Table"), label="tab:classifiers"), include.rownames =FALSE )
@

@@

Define $C_{u,z}$ to the be the classifier score for user $u$ for classifier $z$ where $z$ is an index of the 1,851 classifiers. Then:

@@

The weights for this will be $(1 - \rho_{u,k})^{-1}$ where $\rho_{u,k}$ is the correlation between user $u$ and user $k$. The number of neighbors to use $k$ will be determined by cross-validation on a user-to-user basis. In the end $z_{u,i}$ will be the weighted average of the k-nearest-neighbors scores for user $u$ and game $i$, as given in the equation below (where $u_{[j]}$ is the user with the $j^{\text{th}}$ highest correlation between themselves and user $u$):

\begin{equation}
z_{u,i} = \frac{\sum_{j = 1}^{k} \epsilon_{u_{[j]},i}^{(3)} \cdot \frac{1}{1 - \rho_{u,u_{[j]}}}}{\sum_{j = 1}^{k}\frac{1}{1 - \rho_{u,u_{[j]}}}}
\end{equation}

\subsubsection{Back to Rating}
From what we've produced above in equations (2)-(9), of the estimated rating for user $u$ and game $i$ is given by:

@@

The optimization will use ten-fold cross validation, wherein the data is randomly divided into 10 separate sections of roughly equal size. Then for each of the 10 sections, we'll treat the section as a test set and the other 9 to use as a training set. $\widehat{\theta}_g$ is fit first, and then from a grid of $\alpha_{game}$ values (where $\alpha_{game} \in [1,10000]$), a value of $\widehat{\theta}_i$ is produced for each of the $\alpha_{game}$ in the grid. For each of the $\widehat{\theta}_i$ that are estimated, we'll use the section that wasn't in the training set, the RMSE is calculated here by:
\begin{equation}
\text{RMSE} = \left(\frac{ \sum (r_{u,i}^{(1)} - (\theta_g + \theta_i))^2}{n}\right)^{\frac{1}{2}}
\end{equation}

@@

\begin{figure}\centering
<<k_optim, echo = F, out.width='0.45\\textwidth'>>=
load("k_plot")
k_plot
@
\caption{\label{fig:k} RMSE of candidate k values. For this player, 18 is the optimal value.}
\end{figure}

\section{Technical Implementation} 
This algorithm is implemented in R \citep{rcite}  using shiny \citep{shiny} as a vehicle for a simple, easy to use user interface. Additionally, the packages RSQLite \citep{RSQLite}, dplyr \citep{dplyr}, and magrittr \citep{magrittr} were used. Behind the scenes, the data is stored in a data base with six tables: A player key table, which relates the players information to a unique player userid; A game key table, which relates game information to a unique game id; A ratings table which stores the ratings (a score from 1-10) along with the userid of the person who rated it and the game id which the rating is for; the classifiers table, relates the game id to characteristics about the game that will be useful in the classifier aggregation and k-nearest-neighbors section; the predicted ratings table, which will store predicted ratings if ratings have already been fit for a particular user; and the aggregated classifier ratings for each user. This data storage will allow for ease of implementation: we only really need the ratings table and the classifier table to do all the work, and the key tables are really only needed to display the information to the user in a format which they will understand.

@@

\begin{figure}\centering
<<subdom_plot, echo = FALSE, fig.width = 4, fig.height = 4, out.width='0.5\\textwidth'>>=
load("classifiers_plot")
out
@
\caption{\label{fig:subdplot} A player preference plot for subdomains for the user cwmassey.}
\end{figure}
